Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-07-16 doc/main_jfm.tex
group editing of paper

The second part of the imposed forces and torques comes from repulsion
between proximal particles. We define 
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    (\xx - \aa_i)^{\perp} \cdot 
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
\end{align}
where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
pair of particles. The repulsion profile $P(r)$ is zero for distances
$r$ larger than a repulsion length scale $\rho_0$. As
such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
sufficiently large to prevent particle collisions. The total imposed
force and torque are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  }
    \label{figure2}
\end{figure}

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N58_rupt_0.pdf}
\includegraphics[height=1.2in]{N58_rupt_200.pdf}
\includegraphics[height=1.2in]{N58_rupt_400.pdf}
\includegraphics[height=1.2in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}

@@

@@

\subsubsection{Shear Flow}
Two vesicles in a shear flow is resented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level. With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$. 
An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned. In other words, the the adhesive behavior will be absent when two vesicles are centered 
at a different level and are well separated in $y$-direction.

>>>>

The second part of the imposed forces and torques comes from repulsion
between proximal particles. We define 
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%  \\
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    (\xx - \aa_i)^{\perp} \cdot 
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
\end{align}
\todo[inline]{Repulsion force is a function of only the distance between
the Janus particles instead of the integral around the particles.}
where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
pair of particles. The repulsion profile $P(r)$ is zero for distances
$r$ larger than a repulsion length scale $\rho_0$. As
such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
sufficiently large to prevent particle collisions. The total imposed
force and torque are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}
  \todo[inline]{Put pressure of each of the two configurations below
  this.}
  \caption{Vesicle relaxes under a quiescent flow. (a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay. (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
  }
    \label{figure2}
\end{figure}

@@

\todo[inline]{Introduce dimensionless shear rate here}

@@

\todo[inline]{Figure/Table of the friction coefficient for different
shear rates}

@@

\todo[inline]{Stream lines not right. Need to subtract a constant
velocity instead of the background flow.}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.4in]{N58_rupt_0.pdf}
\includegraphics[height=2.4in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2.4in]{N58_rupt_400.pdf}
\includegraphics[height=2.4in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}

@@

\subsubsection{Shear Flow}
Two vesicles in a shear flow is presented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level. With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$. 
An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned. In other words, the adhesive behavior will be absent when two vesicles are centered 
at a different level and are well separated in $y$-direction.

\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
JCP paper by Rahimian, Veerapaneni, and Biros.}

@@
